Flexibility of interactions depends on habitat suitability

### 2019-06-14 paper/manuscript.Rmd
Some informal checks for species that appear as both plants and pollinators

@@

From the remaining `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names, we were able to identify and the correct missspelling of `r format(n_sp_corrected_typos, big.mark = ",")` organism names. 
Furthermore we found alternative names for `r format(n_sp_with_synonyms, big.mark = ",")` species. 
Most commonly, due to the name being an invalid or not accepted synonym of a species, subspecies, or plant variety (\@ref(tab:tab-sp-synonym-reasons)). 
We were unable to automatically correct `r format(n_sp_not_found, big.mark = ",")` names in the databases.

>>>>

spp %>%
  distinct(sp_name, guild, loc_id) %>%
  group_by(sp_name) %>%
  mutate(n_guilds = n_distinct(guild)) %>% 
  inner_join(checked_sp_names, by = c("sp_name" = "queried_sp_name")) %>% 
  filter(n_guilds > 1) %>% View
  n_distinct(sp_name)

@@

From the remaining `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` scientific names we were unable to validate, we were able to identify and the correct `r format(n_sp_corrected_typos, big.mark = ",")` spelling mistakes. 
These mistakes were corrected automatically used by fuzzy matching with the canonical names in the Global Names Resover database. 
Furthermore we found alternative names for `r format(n_sp_with_synonyms, big.mark = ",")` species. 
Most commonly, due to the name being an invalid or not accepted synonym of a species, subspecies, or plant variety (\@ref(tab:tab-sp-synonym-reasons)). 
We were unable to automatically correct `r format(n_sp_not_found, big.mark = ",")` names in the databases.
